%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\usepackage[none]{hyphenat}

%\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{tomas}{kislan}{c++ \& javascript \& sql developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Bulharska 26
Bratislava 821 04
Slovak Republic
~
+421 918 797 745
~
\href{mailto:kislan.tomas@gmail.com}{kislan.tomas@gmail.com}
\section{languages}
slovak mother tongue
english fluency
german learning
\section{programming}
NodeJS, Express
Angular, React, Redux
Docker (compose)
C++, Boost, Qt \& QML
Python, Robot Framework
PL/SQL, PL/pgSQL
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2014 - Now}
{Software Developer @ Kistler}
%{global leader in dynamic pressure, force, torque, and acceleration measurement}
{Bratislava, Slovakia}
{\emph{Global leader in dynamic measurement technology} \\
Working in an agile team on both \textbf{C++} backend and \textbf{Javascript} (\textbf{ReactJS}, AngularJS) frontend parts of an application running on an embedded device, which is being used for monitoring and controlling of plastic injection process.
\\
Maintaining a custom linux distribution (using \textbf{Yocto}/OpenEmbedded), including multiple background linux services, e.g. web server, logging, etc.
\\
Configuring and maintaining a quality development environment, including continuous integration process, using \textbf{Docker}, \textbf{Jenkins}, etc.
}
\entry
{2010 - 2014}
{Solutions Developer @ Erste Group IT SK}
{Bratislava, Slovakia}
{\emph{Subsidiary company of Slovenska Sporitelna, developing banking system} \\
Design and development of new \textbf{multi-agent transfer system}, pluggable into the existing middleware, with use of asynchronous and multi-threaded programming paradigm.
\\
It's being used as an alternative to commercial (mostly Java) \textbf{ETL} tools, to transfer data between multiple systems, including \textbf{DWH}, as it performed at least 2x faster when transferring data between databases.

\begin{itemize}
\item Huge emphasis placed on extensibility, simple configurability, and performance. 
\item Deployment and maintenance on multiple different operating systems, such as Linux, Windows, OS X, HP-UX, AIX, Solaris.
\item Minor development in python and shell, mainly to support testing, and PL/SQL to integrate into the middleware.
\item Mentoring summer interns, and helping them with C++ comprehension.
\end{itemize}}

%------------------------------------------------
\entry
{2010}
{SOOP}
{Bratislava, Slovakia}
{\emph{Summer Intern} \\
Comparing, and creating test cases for multiple compression libraries against multiple file types, for archiving purposes.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{projects}

\begin{entrylist}
%------------------------------------------------
\entry
{2016 - Now}
{DockMan}
{Docker web management}
{\url{https://gitlab.com/tkislan/dockman}
\\
OSS project
\\
Material design, user friendly web management of docker engine.
\\
NodeJS and ReactJS + Redux application.
}
%------------------------------------------------
\entry
{2016 - Now}
{Metropolitan Real}
{Reality office web site}
{\url{http://www.metropolitanreal.sk}
\\
Material design ReactJS application, with a NodeJS backend, backed up by PostgreSQL database. Implemented server-side rendering for faster page rendering, and Search Engine Optimization. Searching through properties is boosted by Postgres Trigram extension, which is a very effective way for measuring the similarity of words in many natural languages. 
}
%------------------------------------------------
\end{entrylist}

\newpage

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2011 - 2014}
{Masters {\normalfont of Science}}
{Comenius University, Bratislava}
{Specialization in Applied Informatics\\
\emph{Implementation of Offline Transfer System pluggable into batch middleware}\\ 
Masters thesis and a work project. Fast performant transfer adapter, essentialy an ETL tools.}
%------------------------------------------------
\entry
{2008 - 2011}
{Bachelor {\normalfont of Science}}
{Slovak University of Technology, Bratislava}
{Specialization in Informatics}
%------------------------------------------------
\entry
{2014 - Now}
{Conferences}
{Worldwide}
{Attending different conferences on a yearly basis. E.g. webexpo, fosdem, craft, etc.}
\end{entrylist}
%------------------------------------------------

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{technical skills}
\begin{entrylist}
\entry
{C++}
{Middleware and embedded applicaitons}
{5 years}
{Cross-platform application development, using various 3rd party libraries, e.g. \textbf{Boost}, Qt/QML, OpenSSL, OCI etc. Ability to maintain and support complex applications through various different platforms. Practical usage of \textbf{C++14} standard. Performance tuning using gperf, valgrind, etc.}

\entry
{Javascript}
{Experience with larger single page applications}
{3 years}
{Development of a complex embedded application in AngularJS, but nowadays striving to \textbf{ReactJS} \& \textbf{Redux}.
\\
Design and development of \textbf{NodeJS} backend with rest api endpoints using Express. Using ReactJS server-side rendering to increase search index of search engine crawlers. Integrating \textbf{C++} code into \textbf{NodeJS (V8 api)}.
\\
Practical knowledge of \textbf{webpack}, and it's internals, including a development of custom plugins.}

\entry
{Docker}
{Development and production deployment}
{2 years}
{Setting up cross-platform development environment with \textbf{docker-compose}, building production images, and managing deployment of multiple containers.}

\entry
{Python}
{Scripting \& Robot Framework}
{2 years}
{Used to create testing scripts, to assist in development of more complex C++ applications. Proved useful in prototyping several features. Writing simple simulator applications. Extending Robot Framework with custom embedded application requirements.}

\entry
{Databases}
{Oracle, PostgreSQL, \& MongoDB}
{3 years}
{Basic knowledge of database internal processes, ability to tune the performance. Used to implement utility packages to handle integration, and to maintain and monitor existing software. Advanced knowledge of \textbf{PL/SQL} and \textbf{PL/pgSQL}.}

\entry
{Linux, Yocto}
{Development OS, Maintenance of custom distribution}
{2 years}
{Experienced with building custom distribution using the Yocto/OpenEmbedded build framework,
advanced linux OS administration, including configuring and maintaining various linux services.}

\end{entrylist}

%\newpage

%----------------------------------------------------------------------------------------
%	LEADERSHIP SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{leadership skills}

\begin{entrylist}
%------------------------------------------------
\entry
{2013 - 2014}
{Internship mentor}
{}
{Mentoring two interns (in separate timelines), in creating the new components to be later used in the existing transfer adapter, running in the production environment. Delegating and overseeing work being done, while providing feedback and advices.}

\end{entrylist}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} GUI application development, raspberry pi \& odroid, bleeding edge web technologies
\\
\textbf{personal:} volleyball, biking, fitness, books, my vw golf

%----------------------------------------------------------------------------------------

\end{document}
